\documentclass [12pt] {article}

\usepackage {fontawesome5}
\usepackage {fontspec}
\usepackage {geometry}
\usepackage {graphicx}
\usepackage {hyperref}
\usepackage {titlesec}
\usepackage {xcolor}

\geometry {a4paper, margin=20mm}
\hypersetup {hidelinks}
\parindent 0mm
\setmainfont {Liberation Serif}
\thispagestyle {empty}
\titleformat {\section} {\large \ColorAccent} {} {0mm} {} [\SectionLine]
\titlespacing {\section} {0mm} {\baselineskip} {0mm}

\newcommand \At {@}

\newcommand \Name {Dmitry Kalyukov}
\newcommand \Position {Python Developer}
\newcommand \Email {dmitrykalyukov\At gmail.com}
\newcommand \Phone {+7\,000\,000\,00\,00}
\newcommand \LinkedIn {dmitrykalyukov}
\newcommand \GitHub {dmitrvk}

\newcommand \CloserUnderline [1] {\underline {\smash {#1}}}
\newcommand \SectionLine {\hrule \medskip}
\newcommand \ColorAccent {\addfontfeature {Color = 373737}}

\begin {document}

{\Large \ColorAccent \Name}
\medskip

{\large \ColorAccent \Position}
\bigskip

\faEnvelope [regular]\enspace \href {mailto:\Email} \Email \hfill
\faPhone*\enspace \Phone \hfill
\faLinkedinIn\enspace
\href {https://linkedin.com/in/\LinkedIn} {\CloserUnderline \LinkedIn} \hfill
\faGithub\enspace
\href {https://github.com/\GitHub} {\CloserUnderline {\GitHub}}

\bigskip

Kaliningrad, Russia \quad~Age 22

\section {Experience}

\href {https://ruyou.ru} {\underline {RuYou.Ru}}

\emph {Python Developer}

Sep 2020 -- Feb 2021

I've been working remotely for several months
building backends for two mobile applications.\\
Those were an in-store payments app and a food delivery app.\\
I created APIs for client side
and implemented several integrations with external systems.\\
I communicated
with a frontend developer, project managers, and other team members.

\smallskip

Python / Django \\ PostgreSQL \\ Redis

Set up automated tests with GitLab Pipelines.

Deployed with Docker Swarm mode.

\bigskip

\href {https://www.mymusichere.me} {\CloserUnderline {www.mymusichere.me}}
(pet project)

\emph {Web app for sharing personal sheet music collection}

I created the web application,
deployed it on the web server
and set up CI\hspace{0.2mm}/\hspace{0.2mm}CD with GitHub Actions.

\bigskip

\href {https://pypi.org/project/smth} {\CloserUnderline {smth}}
(pet project)

\emph {Command-line tool for scanning books and handwriting on Linux}

I created the CLI application in Python
and published it on the Python Package Index.

\section {Education}

2017--2021

Kaliningrad State Technical University

Applied Information Technology

\bigskip

\emph {Additional}:

2015--2016

Samsung IT School

I learned the basics of programming
and made an Android application as the final individual project.

\section {About}

English language is the primary tool
I use on a daily basis when doing my work.

I work preferably with Linux systems.

LaTeX system is one of my favorites
when it comes to writing documents.

I also play the piano and create music.

\end {document}
